Landscape composition and beneficial insects

### 2020-06-10 manuscript/manuscript_outline.Rmd
Worked on Discussion

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, p[loc=='Pivot'])`, `r with(opilLinTerms, p[loc=='Wetland'])`)  
  + However, unlike _P. melanarius_ or _P. pardosa_, _P. opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`)
  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`, `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
  + The temporal and spatial components, as in the other two species, were both very strong (both p = `r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
  + Together, these results indicate that _P. opilio_ activity density is influenced by large-scale geographic patterns rather than landscape composition
  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance

@@

* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, and responded most strongly to urban and tree/shrub cover
  + _P. melanarius_ is found in a wide variety of habitats, but tends to prefer agricultural fields [@larsen2003]
  + Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988, @fournier2002, but see @hatten2007]
 + In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland/wetland as late-season sink may represent _P. melanarius_ moving to overwintering habitat at the end of the season
 + We also identified several other candidate land cover types as early- and mid-season sources of _P. melanarius_, namely urban, pasture, and pulse crops (primarily lentils in Alberta)
 + The roles that carabids play in pulse crops is not well-studied, but carabids are known predators of pea-leaf weevils (_Sitona lineatus_) on other Fabacea [@hamon1990], so it is possible that pulses represent a source of spill-over
 + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_ (_Bembidion quadrimaculatum_, @vankosky2011)
 <!-- + Carabid diversity is higher in no-till agriculture [@bourassa2008, @puech2014] -->

@@

* The harvestman _Phalangium opilio_ did not respond to landscape composition

@@

* There was a strong temporal component to the landscape effects, meaning that it is important to consider how sinks and sources may change over the season
  + We did not consider the influence of previous years' crops, although carabids tend to be more abundant in areas of high crop rotation [@busch_Msc, @bertrand2015]

>>>>

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, p[loc=='Pivot'])`, `r with(opilLinTerms, p[loc=='Wetland'])`)  
  + However, unlike _P. melanarius_ or _P. pardosa_, _P. opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and trees/shrubs (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`)
  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`, `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
  + The temporal and spatial components, as in the other two species, were both very strong (both p = `r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
  + Together, these results indicate that _P. opilio_ activity density is influenced by large-scale geographic patterns rather than landscape composition
  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance

@@

* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, and responded most strongly to urban and tree/shrub cover
  + _P. melanarius_ is found in a wide variety of habitats, but tends to prefer agricultural fields [@larsen2003]
  + Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007]
 + In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland/wetland as late-season sink may represent _P. melanarius_ moving to overwintering habitat at the end of the season
 + We also identified several other candidate land cover types as early- and mid-season sources of _P. melanarius_, namely urban, pasture, and pulse crops (primarily lentils in Alberta)
 + The roles that carabids play in pulse crops is not well-studied, but carabids are known predators of pea-leaf weevils (_Sitona lineatus_) on other Fabacea [@hamon1990], so it is possible that pulses represent a source of spill-over
 + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011]
 <!-- + Carabid diversity is higher in no-till agriculture [@bourassa2008, @puech2014] -->

@@

* _Phalangium opilio_ activity density did not respond to landscape composition, aside from pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and a weaker response to trees/shrubland (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`) 
  + _P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011]
  + In particular, it is largely found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc]
  + Our results show that _P. opilio_ migrated into pastures
  + It is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc]
  + We found the opposite pattern (albeit weakly): _P. opilio_ appears to migrate into forests

@@

* There was a strong temporal component to the landscape effects, meaning that it is important to consider how sinks and sources may change over the season
  + We did not consider the influence of previous years' crops, although carabids tend to be more abundant in areas of high crop rotation [@busch_Msc; @bertrand2016]
